Modern Statistical Methods --- Example Sheet 1

### 2020-10-23 distribution_theory/distribution_ES1.tex
finished msm example sheet 1git add . #partyyyy

\begin{solution}
	Since $\phi \in \DD(X)$, we know that $\supp\phi \subseteq \clos{B_N}$ for some $N \in \NN$. Now, suppose $\norm{h} < 1$, then
	\[
	\phi(x+h) \neq 0 \implies \norm{x + h} \leq N \implies \norm{x} \leq \norm{x + h} + \norm{h} \leq N + 1, 
	\]
	so if we define $\psi_h(x) = \phi(x+h)$ then we know that $\supp\phi_h \subseteq \clos{B_{N+1}}$.

@@

	Now let $\beta$ be a multi-index and define $C \ceq \frac{1}{N!} \max_{\abs{\alpha} = N+1, x \in \RR^n} \abs{(\pt^{\alpha + \beta})\phi(x)}$ (note that $C$ exists and is finite since all partial derivatives of $\phi$ have compact support), then we have
	\begin{align*}
	\abs{\pt^\beta R_N(x, h)} &= \abs{\pt^\beta \sum_{\abs{\alpha} = N+1} \frac{h^\alpha}{\alpha!}(N+1)\int_0^1 (1-t)^N (\pt^\alpha\phi)(x + th)\dd{t}} \\
	%&= \abs{\sum_{\abs{\alpha} = N+1} \frac{h^\alpha}{\alpha!}(N+1) \cdot \pt^\beta\int_0^1 (1-t)^N (\pt^\alpha\phi)(x + th)\dd{t}} \\
	&\overset\star= \abs{\sum_{\abs{\alpha} = N+1} \frac{h^\alpha}{\alpha!}(N+1) \int_0^1 (1-t)^N (\pt^{\alpha + \beta}\phi)(x + th)\dd{t}} \\
	&\leq \sum_{\abs{\alpha} = N+1} \frac{\abs{h^\alpha}}{\alpha!}(N+1) \int_0^1 (1-t)^N \abs{\qty(\pt^{\alpha + \beta}\phi)(x+th)} \dd{t} \\
	&\leq \qty[\max_{\abs{\alpha} = N+1, x \in \RR^n} \abs{(\pt^{\alpha + \beta})\phi(x)}] \sum_{\abs{\alpha} = N+1} \frac{\abs{h^\alpha}}{\alpha!} (N+1) \\
	&\leq C (N+1)! \sum_{\abs{\alpha}= N+1}\frac{\abs{h^\alpha}}{\alpha!} = C(\abs{h_1} + \dotsb + \abs{h_n})^{N+1}.
\end{align*}
Since this upper bound does not depend on $x$, we also have
\[
\sup_x \abs{\pt^\beta R_N(x, h)} \leq C(\abs{h_1} + \dotsb + \abs{h_n})^{N+1}, 
\]
and we conclude that
\[ 
\frac{\sup_x \abs{\pt^\beta R_N(x, h)}}{\norm{h}^N} \leq \frac{C(\abs{h_1} + \dotsb + \abs{h_n})^{N+1}}{\norm{h}^N} \leq \frac{C N^{N+1} \norm{h}^{N+1}}{\norm{h}^N} = CN^{N+1} \norm{h} \to 0, 
\]
and therefore that $\pt^\beta R_N(x, h) = o(\norm{h}^n)$ for all multi-indices $\beta$. 
\end{solution}
\end{document}

>>>>

\begin{proof}
	Since $\phi \in \DD(X)$, we know that $\supp\phi \subseteq \clos{B_N}$ for some $N \in \NN$. Now, suppose $\norm{h} < 1$, then
	\[
	\phi(x+h) \neq 0 \implies \norm{x + h} \leq N \implies \norm{x} \leq \norm{x + h} + \norm{h} \leq N + 1, 
	\]
	so if we define $\psi_h(x) = \phi(x+h)$ then we know that $\supp\phi_h \subseteq \clos{B_{N+1}}$.

@@

	Now let $\beta$ be a multi-index and define $C \ceq \frac{1}{N!} \max_{\abs{\alpha} = N+1, x \in \RR^n} \abs{(\pt^{\alpha + \beta})\phi(x)}$ (note that $C$ exists and is finite since all partial derivatives of $\phi$ have compact support), then we have
	\begin{align*}
	\abs{\pt^\beta R_N(x, h)} &= \abs{\pt^\beta \sum_{\abs{\alpha} = N+1} \frac{h^\alpha}{\alpha!}(N+1)\int_0^1 (1-t)^N (\pt^\alpha\phi)(x + th)\dd{t}} \\
	%&= \abs{\sum_{\abs{\alpha} = N+1} \frac{h^\alpha}{\alpha!}(N+1) \cdot \pt^\beta\int_0^1 (1-t)^N (\pt^\alpha\phi)(x + th)\dd{t}} \\
	&\overset\star= \abs{\sum_{\abs{\alpha} = N+1} \frac{h^\alpha}{\alpha!}(N+1) \int_0^1 (1-t)^N (\pt^{\alpha + \beta}\phi)(x + th)\dd{t}} \\
	&\leq \sum_{\abs{\alpha} = N+1} \frac{\abs{h^\alpha}}{\alpha!}(N+1) \int_0^1 (1-t)^N \abs{\qty(\pt^{\alpha + \beta}\phi)(x+th)} \dd{t} \\
	&\leq \qty[\max_{\abs{\alpha} = N+1, x \in \RR^n} \abs{(\pt^{\alpha + \beta})\phi(x)}] \sum_{\abs{\alpha} = N+1} \frac{\abs{h^\alpha}}{\alpha!} (N+1) \\
	&\leq C (N+1)! \sum_{\abs{\alpha}= N+1}\frac{\abs{h^\alpha}}{\alpha!} = C(\abs{h_1} + \dotsb + \abs{h_n})^{N+1}.
\end{align*}
Since this upper bound does not depend on $x$, we also have
\[
\sup_x \abs{\pt^\beta R_N(x, h)} \leq C(\abs{h_1} + \dotsb + \abs{h_n})^{N+1}, 
\]
and we conclude that
\[ 
\frac{\sup_x \abs{\pt^\beta R_N(x, h)}}{\norm{h}^N} \leq \frac{C(\abs{h_1} + \dotsb + \abs{h_n})^{N+1}}{\norm{h}^N} \leq \frac{C N^{N+1} \norm{h}^{N+1}}{\norm{h}^N} = CN^{N+1} \norm{h} \to 0, 
\]
and therefore that $\pt^\beta R_N(x, h) = o(\norm{h}^n)$ for all multi-indices $\beta$. 
\end{proof}

\begin{question}
	Which elements of $\DD(X)$ can be represented as a power series on $X$? 
\end{question}

\begin{solution}
	It is known that if two power series agree on an open set, they agree on the entire space. Since every $\phi \in \DD(X)$ is identically zero on some open set (outside its support), the only element of $\DD(X)$ with a power series representation is the zero function. 
\end{solution}

\begin{question}
	Prove the $C^\infty$ Urysohn lemma: if $K$ is a compact subset of $X \subseteq \RR^n$, show that one can find a $\phi \in \DD(X)$ such that $0 \leq \phi \leq 1$ and $\phi = 1$ on a neighborhood of $K$. 
\end{question}

\begin{solution}
	Let $K \subseteq U_1$. Define $U_2 \ceq U_1 + B(0, 1)$ and let $\chi = \ind_{U_2}$. Now let $\psi \in \DD(\RR^n)$ satisfy $\int_{\RR^n} \psi \dd{x} = 1$ and $\supp\psi \subseteq B(0, 1)$. The we compute
	\begin{align*}
		(\chi * \psi)(x) &= \int_{\RR^n} \chi(y) \psi(x - y) \dd{y} = \int_{U_2} \psi(x - y) \dd{y}.
	\end{align*}
	Clearly, $\chi * \psi \in \DD(X)$, and furthermore, we have for $x \in U_1$ that
	\[
	\int_{U_2} \psi(x - y) \dd{y} = \int_{U_2 - x} \psi(z) \dd{z} \overset\star= 1,
	\]
	since $B(0, 1) \subseteq U_2 - x$. This proves the claim.
\end{solution}

\begin{question}
	Given $T \in \DD'(X)$, the derivative $\pt^\alpha T$ is defined by
	\[
	\ang{\pt^\alpha T, \phi} = (-1)^\abs{\alpha} \ang{T, \pt^\alpha\phi} \quad \forall \phi \in \DD(X). 
	\]
	Show that $\pt^\alpha T \in \DD'(X)$. If $\ord(T) = m$ what can you say about $\ord(\pt^\alpha T)$? 
\end{question}

\begin{proof}
	Let $K \subseteq X$ be compact and $\phi \in \DD(X)$. Since $T$ is a distribution, we know that there exists constants $C, N$ such that
	\[
	\abs{\ang{T, \phi}} \leq C \sum_{\abs{\beta} \leq N} \sup \abs{\pt^\beta \phi}. 
	\]

	Letting $M \ceq \abs{\alpha}$, we find
		\begin{align*}
		\abs{\ang{\pt^\alpha T, \phi}} &= \abs{\ang{T, \pt^\alpha\phi}} \leq C \sum_{\abs{\beta} \leq N} \sup \abs{\pt^{\alpha + \beta}\phi} \leq C \sum_{\abs{\beta} \leq M + N} \sup \abs{\pt^\beta \phi}.
	\end{align*}
We conclude that $\pt^\alpha T$ is a distribution, and that if $\ord(T) = m$, $\ord(\pt^\alpha T) \leq m + \abs{\alpha}$. 
\end{proof}

\begin{question}
	Given $T \in \DD'(X)$ and $f \in C^\infty(X)$, prove that for each multi-index $\alpha$
	\[
	\pt^\alpha(Tf) = \sum_{\beta \leq \alpha} \binom{\alpha}{\beta} \pt^\beta f \pt^{\alpha - \beta}T
	\]
	in $\DD'(X)$. 
\end{question}

\begin{proof}
	Let $\phi \in \DD(X)$, then by definition we have $\ang{\pt^\alpha(Tf), \phi} = \ang{T, (-1)^\abs{\alpha} f \pt^\alpha\phi}$. Approximate $T$ by a sequence $(\psi_n) \subseteq \DD'(X)$, then we find
	\begin{align*}
	\ang{T, (-1)^{\abs{\alpha}} f \pt^\alpha\phi} &= \lim_{n\to\infty} \ang{\psi_n,  (-1)^{\abs{\alpha}} f \pt^\alpha\phi} = \lim_{n\to\infty}  (-1)^{\abs{\alpha}} \int_X \psi_n(x) f(x) \pt^\alpha\phi(x) \dd{x} \\
	&= \lim_{n\to\infty} \int_X \pt^\alpha (\psi_n(x) f(x)) \phi(x) \dd{x} \\
	&= \lim_{n\to\infty} \int_X \qty(\sum_{\beta \leq \alpha} \binom\alpha\beta\pt^\beta f(x) \cdot \pt^{\alpha - \beta} \psi_n(x)) \phi(x) \dd{x} \\
	&= \lim_{n\to\infty} \sum_{\beta \leq \alpha} \binom\alpha\beta \ang{\pt^\beta f \pt^{\alpha - \beta} \psi_n, \phi} =  \lim_{n\to\infty} \sum_{\beta \leq \alpha} \binom\alpha\beta (-1)^{\abs{\alpha - \beta}} \ang{\psi_n, \pt^\beta f \pt^{\alpha - \beta} \phi} \\
	&= \sum_{\beta \leq \alpha} \binom\alpha\beta (-1)^{\abs{\alpha - \beta}} \ang{T, \pt^\beta f \pt^{\alpha - \beta} \phi} = \sum_{\beta \leq \alpha} \binom\alpha\beta \ang{\pt^\beta f \pt^{\alpha - \beta} T, \phi} \\
	&= \ang*{\sum_{\beta \leq \alpha} \binom{\alpha}{\beta} \pt^\beta f \pt^{\alpha - \beta}T, \phi}. 
	%&= \lim_{n\to\infty} \ang*{\sum_{\abs{\beta} \leq \abs{\alpha}} \binom\alpha\beta \pt^\beta f\cdot \pt^{\alpha - \beta} \psi_n, \phi} = \lim_{n\to\infty} \sum_{\abs{\beta} \leq \abs{\alpha}
	\end{align*}
\end{proof}

\begin{question}
	Let $(x_k)$ be a sequence in $X$ with no limit point in $X$. Consider the family of linear maps
	$u_\alpha \colon \DD(X) \to \CC$ defined by 
	\[ \ang{u_\alpha, \phi} = \sum_{k=1}^\infty \pt^\alpha \phi(x_k)
	 \]
	 for each multi-index $\alpha$. For what $\alpha$ is $u_\alpha \in \DD'(X)$? What is $\ord(u_\alpha)$? 
\end{question}

\begin{solution}
	Let $K \subseteq X$ be compact. Since $(x_k)$ does not have a limit point, only finitely many of the $x_k$ lie in $K$ (otherwise $(x_k)$ would have a subsequence contained in $K$ which would have a convergent subsequence). Without loss of generality, assume that $x_1, \dotsc, x_n \in K$, and $x_{n+1}, x_{n+2}, \dotsc, \notin K$. Now, for any $\phi \in \DD(X)$ with $\supp(\phi) \subseteq K$ we find
	\begin{align*}
		\abs{\ang{u, \phi}} &= \abs{\sum_{k=1}^\infty \pt^\alpha\phi(x_k)} = \abs{\sum_{k=1}^n \pt^\alpha\phi(x_k)} \leq \sum_{k=1}^n \abs{\pt^\alpha \phi(x_k)} \leq n \cdot \sup \abs{\pt^\alpha\phi} \leq n \cdot \sum_{\abs{\beta} \leq \abs{\alpha}} \sup \abs{\pt^\beta \phi}. 
	\end{align*}
	This shows that $u_\alpha \in \DD'(X)$ for any $\alpha$, with $\ord(u_\alpha) \leq \abs{\alpha}$. We claim that this is an equality, i.e., $\ord(u_\alpha) = \abs{\alpha}$. \TODO How to show??
\end{solution}

\begin{question}
	Find the most general solution to the equations
	\begin{enumerate}[(a)]
		\item $u'  = 1$,
		\item $xu' = \delta_0$,
		\item $(e^{2\pi i x} - 1)u' = 0$
	\end{enumerate}
	in $\DD'(\RR)$. 
\end{question}

\begin{solution}
	Let $\phi \in \DD(X)$. 
	\begin{enumerate}[(a)]
		\item If $u' = 1$ then we find 
		\[
		\int_\RR \phi(x) \dd{x} = \ang{1, \phi} = \ang{u', \phi} = -\ang{u, \phi'},
		\]
		so for any $c \in \RR$ we find by partial integration $\ang{u, \phi'} = - \int_\RR\phi(x) \dd{x} = \int_\RR (x + c) \phi'(x) \dd{x}$. From this we deduce that $u = x + c$ for some $c$. 
	\end{enumerate}
\end{solution}
\end{document}

### 2020-10-23 modern_statistical_methods/msm_ES1.tex
finished msm example sheet 1git add . #partyyyy

\newcommand\XX{\Cal X}

@@

% Frequently used commands
\newcommand{\T}{^\top} % Matrix transpose A\T
\newcommand{\C}{^\complement} % Set complement A\C
\newcommand\ceq\coloneqq % Definitions :=
\newcommand\pow{\Cal P} % Power sets
\newcommand\eps\epsilon
\newcommand\ind{\mathbbm 1} % Blackboard 1 for indicator functions
\newcommand\restr{\mathord\restriction}
\newcommand\TODO{{\color{red} TODO: }}

@@

	Symmetry of $k$ is clear. Define the function 
	\[
	\phi \colon (-\infty, 1) \to \RR \colon x \mapsto (1-x)^{-\alpha}. 
	\]
	Then $\phi$ is continuous, and we can compute its Taylor series around 0. It is computed that 
	\[
	\phi^{(k)}(x) = (1-x)^{-\alpha - k} \prod_{j=0}^{k-1}(\alpha + j) \implies \phi^{(k)}(0) = \prod_{j=0}^{k-1} (\alpha + j). 	\]
	Therefore, the Taylor series of $\phi$ is given by
	\[
	\sum_{k=0}^\infty \qty(\prod_{j=0}^{k-1} (\alpha + j)) \frac{x^k}{k!}, 
	\]
	and its radius of convergence is given by
	\[
	\lim_{k\to\infty} \frac{\frac{1}{k!}\prod_{j=0}^{k-1} (\alpha + j)}{\frac{1}{(k+1)!} \prod_{j=0}^k (\alpha + j)} = \lim_{k\to\infty} \frac{k}{\alpha + k} = 1,
	\]
	so $\phi$ agrees with its Taylor series on $(-1, 1)$. By Cauchy-Schwarz, for $x, x' \in \XX$ we have $x_i\T x_j \leq \norm{x_i} \norm{x_j} < 1$, so we can write for $x, x' \in \XX$
	\[
	k(x, x') = \phi(x\T x') = \sum_{k=0}^\infty \qty(\prod_{j=0}^{k-1} (\alpha + j)) \frac{(x\T x')^k}{k!}.
	\]
	By proposition 4, every term in the sum is a kernel, and therefore the limit is a kernel as well. 
\end{proof}

@@

\begin{question}
	...
\end{question}

\begin{proof}
	content...
\end{proof}

\begin{question}
	...
\end{question}

\begin{proof}
	...
\end{proof}

@@

	To this end, assume $x_1 \leq \dotsb \leq x_n$ (this may require relabeling of the $x_i$ which does not affect positive semi-definiteness of $K$). Now let $\vec f_i$ denote the vector $f_{i1}, \dotsc, f_{i(i-1)} = 0$, $f_{ii}, \dotsc, f_{in} = 1$. 
	\[
	K = \mqty[ x_1 & x_1 & x_1 & \cdots & x_1 \\
	x_1 & x_2 & x_2 & \dotsb & x_2 \\
	x_1 & x_2 & x_3 & \dotsb & x_3 \\
	\vdots & \vdots & \vdots & \ddots & \vdots \\
	x_1 & x_2 & x_3 & \cdots & x_n] = x_1 \vec f_1 \vec f_1\T + (x_2 - x_1) \vec f_2 \vec f_2\T + \dotsb + (x_n - x_{n-1}) \vec f_n \vec f_n\T. 
	\]
	Since this is a nonnegative combination of positive semidefinite matrices, we conclude that $K$ is positive semidefinite. 
\end{solution}
\end{document}

>>>>

\newcommand\XX{\Cal X}
\newcommand\HH{\Cal H}

@@

% Frequently used commands
\newcommand{\T}{^\top} % Matrix transpose A\T
\newcommand{\C}{^\complement} % Set complement A\C
\newcommand\ceq\coloneqq % Definitions :=
\newcommand\pow{\Cal P} % Power sets
\newcommand\eps\epsilon
\newcommand\ind{\mathbbm 1} % Blackboard 1 for indicator functions
\newcommand\restr{\mathord\restriction}
\newcommand\TODO{{\color{red} TODO: }}
\renewcommand\P{^\perp}

@@

	Symmetry of $k$ is clear. Define the function 
	\[
	\phi \colon (-\infty, 1) \to \RR \colon x \mapsto (1-x)^{-\alpha}. 
	\]
	Then $\phi$ is smooth, and we can compute its Taylor series around 0. It is computed that 
	\[
	\phi^{(k)}(x) = (1-x)^{-\alpha - k} \prod_{j=0}^{k-1}(\alpha + j) \implies \phi^{(k)}(0) = \prod_{j=0}^{k-1} (\alpha + j). 	\]
	Therefore, the Taylor series of $\phi$ is given by
	\[
	\sum_{k=0}^\infty \qty(\prod_{j=0}^{k-1} (\alpha + j)) \frac{x^k}{k!}, 
	\]
	and its radius of convergence is given by
	\[
	\lim_{k\to\infty} \frac{\frac{1}{k!}\prod_{j=0}^{k-1} (\alpha + j)}{\frac{1}{(k+1)!} \prod_{j=0}^k (\alpha + j)} = \lim_{k\to\infty} \frac{k}{\alpha + k} = 1,
	\]
	so $\phi$ agrees with its Taylor series on $(-1, 1)$. By Cauchy-Schwarz, for $x, x' \in \XX$ we have $x_i\T x_j \leq \norm{x_i} \norm{x_j} < 1$, so we can write for $x, x' \in \XX$
	\[
	k(x, x') = \phi(x\T x') = \sum_{k=0}^\infty \qty(\prod_{j=0}^{k-1} (\alpha + j)) \frac{(x\T x')^k}{k!}.
	\]
	By proposition 4, every term in the sum is a kernel, and therefore the limit is a kernel as well. 
\end{proof}

@@

\begin{question}
	Consider minimising
	\[
	c(Y, X, f(x_1) + \mu, \dotsc, f(x_n) + \mu) + J(\norm{f}^2_\HH),
	\]
	over $f \in \HH$ and $\mu \in \RR$ where $\HH$ is an RKHS. Here $c$ is an arbirary loss function and $J$ is strictly increasing. Let $k$ be the reproducing kernel of $\HH$. Show that any minimiser $\hat g(\cdot) = \hat f(\cdot) + \hat \mu$ may be written as
	\[
	\hat g(\cdot) = \hat \mu + \sum_{i=1}^n \hat\alpha_i k(\cdot, x_i)
	\]
	where $\hat\alpha_i \in \RR$ for $i = 1, \dotsc, n$. 
\end{question}

\begin{proof}
	As in the proof of the representer theorem, we project $f$ onto $U = \Span\qty{k(\cdot, x_1), \dotsc, k(\cdot, x_n)}$, and find that the problem is equivalent to finding
	\[
	\argmin_{u \in U, \mu \in \RR} c(Y, X, u(x_1) + \mu, \dotsc, u(x_n) + \mu) + J(\norm{u}^2),
	\]
	and writing $u = \sum_{i=1}^n \alpha_i k(\cdot, x_i)$, we find that any minimiser $\hat g$ satisfies
	\[
	\hat g(\cdot) = \hat \mu +  \sum_{i=1}^n \hat\alpha_i k(\cdot, x_i)
	\]
	as required. 
\end{proof}

\begin{question}
	This question proves a result needed for Theorem 7 in the notes. Let $\HH$ be a RKHS of functions on $\XX$ with reproducing kernel $k$ and suppose $f^0 \in \HH$. Let $x_1, \dotsc, x_n \in \XX$ and let $K$ be the kernel matrix $K_{ij} = k(x_i, x_j)$. Show that
	\[
	\qty(f^0(x_1), \dotsc, f^0(x_n))\T = K\alpha,
	\]
	for some $\alpha \in \RR^n$ and moreover that $\norm{f^0}^2_\HH \geq \alpha\T K\alpha$. 
\end{question}

\begin{proof}
	Let $U = \Span\qty{k(\cdot, x_1), \dotsc, k(\cdot, x_n)}$. Then we have $f^0 = u + v$ for some $u \in U, v \in U\P$, and writing $u = \sum_{m=1}^n \alpha_m k(\cdot, x_m)$ we see that 
		\[
	f^0(x_i) = \ang{k(\cdot, x_i), u + v} = \ang{k(\cdot, x_i), u} = u(x_i) = \sum_{m=1}^n \alpha_m k(x_i, x_m) = (K\alpha)_i,
	\]
	and from this it follows immediately that 
	\[
	\norm{f^0}^2 = \norm{u}^2 + \norm{v}^2 \geq \norm{u}^2 = \sum_{i, j} \alpha_i \alpha_j k(x_i, x_j) = \alpha\T K\alpha. 
	\]
\end{proof}

@@

	To this end, assume $x_1 \leq \dotsb \leq x_n$ (this may require relabeling of the $x_i$ which does not affect positive semi-definiteness of $K$). Now let $\vec f_i$ denote the vector $f_{i1}, \dotsc, f_{i(i-1)} = 0$, $f_{ii}, \dotsc, f_{in} = 1$. 
	\[
	K = \mqty[ x_1 & x_1 & x_1 & \cdots & x_1 \\
	x_1 & x_2 & x_2 & \dotsb & x_2 \\
	x_1 & x_2 & x_3 & \dotsb & x_3 \\
	\vdots & \vdots & \vdots & \ddots & \vdots \\
	x_1 & x_2 & x_3 & \cdots & x_n] = x_1 \vec f_1 \vec f_1\T + (x_2 - x_1) \vec f_2 \vec f_2\T + \dotsb + (x_n - x_{n-1}) \vec f_n \vec f_n\T. 
	\]
	Since this is a nonnegative combination of positive semidefinite matrices, we conclude that $K$ is positive semidefinite. 
\end{solution}

\begin{question}
	Let $\HH$ be a RKHS with reproducing kernel $k$. Show that if $h_x \in \HH$ has the property that $\ang{h_x, f} = f(x)$ for all $f \in \HH$, then $h_x(\cdot) = k(\cdot, x)$. 
\end{question}

\begin{proof}
	For any $y \in \XX$ we have
	\[
	h_x(y) = \ang{k(\cdot, y), h_x} = \ang{h_x, k(\cdot, y)} = k(x, y) = k(y, x),
	\]
	from which it follows that $h_x(\cdot) = k(\cdot, x)$. 
\end{proof}

\begin{question}
	Prove that if $k$ is a reproducing kernel for RKHS's $\HH_1$ and $\HH_2$, then $\HH_1 = \HH_2$, so the RKHS is uniquely determined by $k$. \emph{Hint: First argue that it is enough to show the result for $\HH_1 \subseteq \HH_2$. Next consider decomposing each $f \in \HH_2$ as $f = u+ v$ with $u \in \HH_1, v \in \HH_1\P$ and argue that $v = 0$. }
\end{question}

\begin{proof}
	Without loss of generality we can assume $\HH_1 = \HH$, where $\HH$ is the RKHS constructed in the proof of Theorem 5, so $\HH$ is the completion of $\Span\qty{k(\cdot, x) \mid x \in \XX}$. Now we can embed $\HH$ into $\HH_2$ by mapping $k(\cdot, x)$ to $k_x$. Clearly this mapping respects the inner product by construction, so this is a linear embedding. Therefore, we may assume $\HH_1 \subseteq \HH_2$.

	Now suppose $\HH_1 \subseteq \HH_2$ and decompose each $f \in \HH_2$ as $f = u + v$ with $u \in \HH_1$, $v \in \HH_1\P$. By the previous question we know that for every $x$ there exists a unique $k_x$ with $\ang{k_x, f} = f(x)$ for all $f$, and clearly we have $k_x \in \HH_1$.

	Then for each $f \in \HH_2, x \in \XX$ we have (since $k_x \in \HH_1$) that
	\[
	f(x) = \ang{k_x, f} = \ang{k_x, u} + \ang{k_x, v} = \ang{k_x, u} = u(x),
	\]
	which implies $v = 0$. Since this is the case for every $f \in \HH_2$, we conclude that $\HH_1\P = 0$ and therefore $\HH_1 = \HH_2$ (since Hilbert spaces are closed). 
\end{proof}
\end{document}
